Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-10 WRITEUP/ms.tex
update abstract more

\begin{abstract}
We study the dynamical properties of molecular clouds complexes (MC) and their temporal evolution in \flower, a prototypical galaxy
at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
to identify MCs and their sub-structures.
We extract properties such as mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) 
for each MC and 
compare them with those observed in the Milky Way disk, the Galactic center,
and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
The high velocity dispersions found in the MCs of \flower ($\sigma\approx$\,200\,\kms) are comparable to 
those observed in starburst galaxies.
The mass scale of the MCs is on the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the spiral arms of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for  
the molecular substructures, likely resulting from 
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
Virial analysis indicates that the MCs found in the main disk of \flower are unbound, but its substructures have lower virial parameters. 
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
supported by turbulence and rotation on large scale.
We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as result of the weaker stellar feedback 
due to the less frequency \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the former).
MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
as gas is being accreted from the intergalactic medium.
We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are insensitive to the choice of $n_{\rm cut}$, except for the slope of the cumulative 
mass distribution, which steepens with $n_{\rm cut}$. 
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the 
Next Generation Very Large Array (ngVLA)
will provide useful observational data to test our findings and the validity of our simulation to shed
light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

>>>>

\begin{abstract}
We study the dynamical properties of molecular clouds complexes (MC) and their temporal evolution in \flower, a prototypical galaxy
at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
to identify MCs and their sub-structures.
We extract properties such as mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) 
for each MC and 
compare them with those observed in the Milky Way disk, the Galactic center,
and gas-rich starburst galaxies in the local Universe and at the peak epoch of cosmic \SF.
The high velocity dispersions found in the MCs of \flower ($\sigma\approx$\,200\,\kms) are comparable to 
those observed in starburst galaxies.
The mass scale of the MCs is on the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the spiral arms of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely result from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted,
with $\sigma\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for  
the molecular substructures.
The high velocity dispersions likely result from 
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
Virial analysis indicates that the MCs found in the main disk of \flower are unbound, but its substructures have lower virial parameters. 
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
supported by turbulence and rotation on large scale.
We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as result of the weaker stellar feedback 
due to the less frequency \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the former).
MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
as gas is being accreted from the intergalactic medium.
We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are insensitive to the choice of $n_{\rm cut}$, except for the slope of the cumulative 
mass distribution, which steepens with $n_{\rm cut}$. 
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the 
Next Generation Very Large Array (ngVLA)
will provide useful observational data to test our findings and the validity of our simulation to shed
light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}
